%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://hari01584.github.io/portfolio/}{\Large Harishankar Kumar}} & Email : \href{mailto:hari01584@gmail.com}{hari01584@gmail.com}\\
  \href{https://hari01584.github.io/portfolio/}{https://hari01584.github.io/portfolio/} & Mobile : +918872276957 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thapar Institute of \& Engineering  Technology}{Patiala, Punjab}
      {Bachelor of Technology - BTech; 8.62 CGPA}{2020 -- 2024}
    \resumeSubheading
      {Kendriya Vidyalaya No 2}{Ferozepur Cantt, Punjab}
      {XII, PCM;  95\% Boards}{2007 -- 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Smart India Hackathon}{Hyderabad, Telangana}
    {Winner}{SIH 2022}
    \resumeItemListStart
      \resumeItem{Technical Lead}
        {Guided the team through technical aspects of creating project, assigned work to different tech stacks and acted as a coordinator to merge everything into one, managed all the others working in different languages/framework and also helped in practical coding!}
    \resumeItemListEnd


    \resumeSubheading
      {Google Developer Student Club}{Patiala, Punjab}
      {Core Member}{Sept 2021 - Present}
      \resumeItemListStart
        \resumeItem{Quantum Computer Project}
          {Worked in Quantum Computing project and acted as a proof reader and editor for all the study materials and resources provided there.}
        \resumeItem{Events}
          {As a core member helped in many big/small events and different aspects like advertisement, technical, deployment, etc.}
      \resumeItemListEnd

      \resumeSubheading
      {Microsoft Learn Student Chapter}{Patiala, Punjab}
      {Member}{Jul 2021 - Jun 2022}
      \resumeItemListStart
        \resumeItem{Speaker for Gamedev Workshop}
          {Conducted a workshop for juniors on the topic of game-development and especially by using graphics library like sdl2!}
      \resumeItemListEnd

      \resumeSubheading
      {Dev Launchers - Remote}{Austin, Texas, United States}
      {Member}{Feb 2020 - Mar 2021}
      \resumeItemListStart
        \resumeItem{Events Manager}
          {Was event manager for Non profit organization DevLaunchers, promoting game development in early teens using fun and interactive workshops!}
        \resumeItem{Plugins for Minecraft Server}
          {Created minecraft java plugins for community minecraft server of devlaunchers.}
      \resumeItemListEnd

      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {App Developer}{Google Playstore}
      {Indie Developer}{Lifetime}
      \resumeItemListStart
        \resumeItem{XenonE For Blockman GO}
          {Installed on more than quarter million devices \(250k+\) and generated revenues above 10 grands (10,000\$), the application was massive hit and was actively used by more than a hundred thousands users actively at some point!}
        \resumeItem{Vortex Connect - An Online Multiplayer}
          {Recreated the classic minecraft servers hosting application, all the frontend/backend etc were created and application was deployed on the server. More than 16k installs with 1k+ active users and half a thousand testers.}
        \resumeItem{Shapes 2D}
          {A multi-platform game made using graphics library sdl2 and android native.}
      \resumeItemListEnd

    \resumeSubheading
      {Blogs}{Remote}
      {Blogging/Posts}{Lifetime}
      \resumeItemListStart
        \resumeItem{Content Writing}
          {Wrote technical and non technical blogs, which included tutorials, real life experiences, step-by-step walkthrough, demo/proof of concept work etc! \textbf{\href{https://withme.skullzbones.com/blog}{Link of the blog here}}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  % https://withme.skullzbones.com/blog

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{DeSu - Decentralized Survey App}
      {Created a blockchain based application and website for taking anonymous and secure surveys which promotes an open internet ecosystem.}
    \resumeSubItem{Beat-Remix}
      {Mix sound with images to create montage/edits using the rhymthic beats!}
    \resumeSubItem{BubbleBoxModel}
      {A deep learning model and notebooks to identify text bubbles in manga panels. Made using tensorflow and keras!}
    \resumeSubItem{libMcServerProxy}
      {An android library for brodcasting Minecraft servers to your lan without going through hassles of manually doing so! Took a great time and research on networking to create this.}
    \resumeSubItem{RaspMyBerry}
      {Raspberry Pi Moderator and status tool using discord client.}

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
